Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-14 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Ich habe den "Nanoinjection"-Teil in 2 Sätzen zusammengefasst. 
Der ist jetzt da zu finden, wo wir schon sagen, dass wir nichts über SNOM und so sagen werden.

Although recording SICM and FM data independently on different samples under
the same conditions can support conclusions that could not be drawn from data
from a single technique alone \cite{Gesper2017,Lee2013,Lyon2009}, we will
focus on applications were SICM and FM data has been recorded from the same
sample. Furthermore, we focus on far-field FM techniques and do not review the
combination of SICM with nearfield optical microscopy  
\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}.

>>>>

Although recording SICM and FM data independently on different samples under
the same conditions can support conclusions that could not be drawn from data
from a single technique alone \cite{Gesper2017,Lee2013,Lyon2009}, we will
focus on applications were SICM and FM data has been recorded from the same
sample. Furthermore, we focus on far-field FM techniques and do not review the
combination of SICM with nearfield optical microscopy  
\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}. We also do not review
studies, that use the nanopipette for targeted deposition 
\cite{Ying2002,Bruckbauer2007,Bruckbauer2010,Hennig2015} or for injection 
\cite{Hennig2015a} of fluorescent/fluorescently-labeled molecules. As well, as studies, 
where the nanopipette was used for manipulation \cite{Fuentes2012,Wang2020} or as a 
fluorescence-based nanosensor \cite{Piper2006}.

% Vielleicht können wir die letzten beiden Sätze (siehe Absatz darüber) noch einfügen, 
% dann würde das so aussehen, dass die Entscheidung, über diesen Bereich nicht zu berichten 
% gezielt war und nicht dass wir sie vergessen hätten!?
